HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-05 scnn.tex
samll changes

Convolutional Neural Networks (CNNs) are now a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence. Despite their successes, they still are mostly developed and applied to regular Euclidean domains such as those supporting images, audio, or video. For many applications however, the data domain is not regular.
As a response to that fact, we are witnessing an increasing interest in the generalization of CNNs to graphs. Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
In this paper we take the latter view and represent a sampled sphere as a graph, for which we define the convolution and pooling operations.
Spherical maps appear in many applications, such as the study of phenomena on the Earth for meteorologists or on the sky for cosmologists.
A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling. Hence, we present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
\nati{I am not that we should talk about pooling in the abstract. Another angle would be to say that HealPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical Manifold structure and b) pooling is natural.} 
While convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far. 
As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that as been explored previously.
% The filters learned by the HealpixNet are restricted to being radial.
% Michaël: not necessary in the abstract?
We demonstrate the method on a classification problem of mass maps from two cosmological models. 
\nati{Should we specify what are the baselines? I think not.}
A standard benchmark for that problem is to train an SVM on the histograms of map pixel values. Another is to use the power spectral density instead.
HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
Code and examples are available at \todo{\url{https://github.com/xxx}}.
\end{abstract}

@@

\section{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item (yes) Michael, do you agree with the title HealpixNet? I (Michaël) extensively modified the abstract to reflect that it is a special case of graph CNNs tailored to Healpix. Hence I now agree with the title. Feel free to edit. Ideally I'd like to have "graph" in the title (graph CNNs are quite hot these days), but I couldn't find how.
    \item Emphasize the novelty of using it on Helapix in abstract, into and rest of the paper
    \item Finish section on Convolutions on graphs (Michael - Nathanael)
    \item Plot of the new filters from Mass maps (Michael)
    \item (done!, plot to be added) check the power spectrum after smoothing
    \item (done!) upgrade the plot of pooling (Nathanael)
	\item (done!) new plot for network structure (teaser plot) (Michael) What do you think? Todo: link the points on the sphere to the fully connected
    \item add info on comparison with histogram, so that it's just a demonstration
    \item (done!) Figure 1 to be round
    \item finish section on Efficient convolutions (Michael)
    \item conclusions
    \item (done!) new simulations with 3 arcmin smoothing
    \item (done!) simulation with cross-validation for the histogram
    \item (done!) Update result section according to the new simulations...
    \item (done!) simulation PSD
    \item (done!) Results figure, add sigma8
    \item (more or less done!) possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael I am not sure about the heat diffusion example...)
\end{itemize}

\begin{figure*}[!ht]
	\centering
	\includegraphics[width=\linewidth]{figures/architecture}
	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier. A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling. While most operations are agnostic to the data domain, the convolution and down-sampling have to be adapted. In this paper, we propose first to model the sphere with a graph and to perform the convolution on the graph. Graphs are versatile data structures which can model any sampling, even irregular or partial. Second, we propose to exploit a hierarchical pixelization of the sphere for the pooling operation. It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.
    \nati{Great plot! Could you make the sphere round? If you use the current code in paper plot, they will be.}
    }
\end{figure*}

@@

To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling. The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which is efficient and can adapt to any sampling of the sphere. Using a k-nearest neigboors graph, the convolution operation costs $\mathcal{O}(n)$ operations, where $n$ is the number of pixels. That is the lowest possible complexity for convolution without approximations (e.g. by sketching).
The flexibility of modeling the data domain with a graph allows, for example, to easily model data which only spans a part of the sphere, or data which is not uniformly sampled.
Our hierarchical pooling strategy exploits a hierarchical pixelization of the manifold to analyze the data at multiple scales. Such hierarchical pixelizations of the sphere have been well studied.

@@

We give a practical demonstration of the application of our package to cosmological model discrimination using convergence maps, similar to \citep{schmelze2017cosmologicalmodel}.
In a simplified scenario, we classify convergence maps on parts of a sphere into two cosmological models.
These models were designed to have the same power spectrum in range $\ell < 1000$.
We compare the performance of the spherical CNN to a baseline algorithm, an SVM classifier which takes pixel histograms or Power Spectrum Densities (PSD) of these maps as input.
The comparison is made as a function of noise level on convergence maps and area of the sphere used. Results show that our model is better at discriminating the maps, is more resilient to noise, and \todo{is faster?}.
\nati{I do not think we should argue for speed gain in this paper. We are probably much more efficient than scnns with the convolution done in the spectral domain. However compared to tradiationl methods, we are in most of the case slower.}

@@

The first approach, leveraging the continuous spherical convolution, has been
proposed by~\cite{cohen2017convolutional,cohen2018spherical}. The goal of
these contributions it to use a rotational equivariant convolution on the
sphere, i.e. a rotation of the input implies the same rotation of the output.
The resulting convolution is performed by a spherical Fourier transform (i.e.
a projection on the spherical harmonics), a  multiplication in the spectral
domain and an inverse spherical Fourier transform. Hence the main
computational cost of a convolution comes from the two Fourier transforms.
Fortunately, the Fourier transform can be accelerated for special samplings
set (theoretically including HealPix, \cite{mohlenkamp1999fast,rokhlin2006fast}). 
The main advantage of this
approach is that it provides a mathematically well defined rotational
equivariant network. Nevertheless, even with these Fourier transform
acceleration, the convolutions remain expensive in comparison to a traditional
2-dimensional convolution, limiting the practical use of this approach.
\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the healpix Fourier transform to get the constants
\nati{@mdeff: for the complexity we probably have $\mathcal{O}(n)$ instead of $\mathcal{O}(n^{3/2})$ (let assume that we have $\approx n^{1/2}$ points allong both axis, computation of the SO3 FFT is composed of 1) $n^{1/2}$ FFTs for a total cost of $n \log (n)$ and 2) $n^{1/2}$ matrix multiplications of size $n^{1/2}$ for a total cost of $n^{3/2}$)}
}
While a comparison is theoretically possible, the experiments
of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
do not provide any code for the Healpix one. Hence, a practical comparison is
not possible. We also note that this approach cannot be trivially accelerated
if only one part of the sphere is used. This is impractical in the field of
cosmology as the data often observed only on a subpart of the sphere. 
One could still pad the unused part of the sphere with 0. However, this would significantly increase the computational cost of the method.
\nati{@mdeff: do you think we can say the method would be too slow for our dataset even without trying it? I am not so sure...}
\todo{slow: full sky maps are composed of millions of points. partial maps are hard to process}

@@

In an attempt to get the best of the two first approaches, we follow a third
direction. We use a graph to adapt to the particular structure of the sphere.
While the convolution remains efficient, it still captures well the spherical
structure and is particularly adapted to the HealPix sampling.

The use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graph} as well. The authors map omnidirectional images to the sphere, with the goal of correcting for distortions induced by the lens used for the acquisition.
Besides the different application covered by the paper, there are two important
differences. First the sampling is different as~\cite{khasanova2017graph} uses a
grid. Second, it uses a different graph CNN based on a different parametrization
of the convolution kernel.

@@

HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere. As suggested in the name, this pixelization produces a subdivision of a spherical surface in which each pixel covers the same surface area as every other pixel.
The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}). As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
High-resolutions HEALPix maps easily reach millions of pixels. \figref{example_maps} shows two examples.
Another property of the HEALPix grid is that the pixel centers, represented by the black dots in \figref{pooling}, occur on a discrete number of rings of constant latitude (the number of which depends on the resolution).
\nati{The figure is beautiful, but should we really show it? If we target cosmologists, we can simply list some type of data. If we target a more broad audience, maybe it makes sense to provide some illustration.}

@@

In the classical 2-dimenstional convolution, each pixel is connected with the
same weight to its 4 closest neighbors. We use a weighted undirected graph to
generalize this idea to the ubiquitous HealPix
sampling~\citep{gorski2005healpix}.  Each pixel is represented by a node
(vertex) connected to his $8$ or $7$ closest neighbors.\footnote{For some
pixels, the $8^{th}$ nearest neighbor is not well defined.} Given the set of
nearest neighbors, we define the weight matrix $W$ using the following scheme
\begin{equation}
W[i,j]=\begin{cases}
e^{-\frac{\|x_i-x_j\|_2^2}{\sigma^2}} & \text{if pixels $i$ and $j$ are connected, and}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}
\todo{why not $1/d$? See Pascal's paper, \nati{ The question is: is $1/d$ also good when we have 7/8 neighboors instead of 4? Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment. We probably do not have to change any parameter though... @mdeff: do you think we should try this for this paper? Or we keep that for the next one.}}
Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$
on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected
pixels $i$ and $j$. This weighting scheme is important as the distances between
pixels varies due to the small sampling irregularities. Some of the
irregularities have been highlighted in the graph displayed in
\figref{healpix_graph_4}.

@@

\begin{figure}[!ht]
\centering
% \includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
\vspace{-0.5cm}
\includegraphics[width=0.35\textwidth]{figures/half_graph_4.pdf}
\vspace{-0.5cm}
\caption{
Top view of a Healpix graph for half the sphere using an nside parameter of $4$.
Nodes with 7 neighbors are highlighted. \label{fig:healpix_graph_4}
}

@@

As shown in \figref{graph_harmonics}, it turns out that using the graph
construction described above, the graph Fourier harmonics resemble the
classical spherical harmonics giving us an indication that the graph is able to
capture the spherical properties of the Healpix sampling. This topic is further discussed in \ref{sec:spherical_harmonics}.

@@

\paragraph{Example:}
Let us consider the heat diffusion problem
\begin{equation} \label{eqn:heat_equation}
\L \b{f}(t) = \tau \partial_t \b{f}(t),
\end{equation}
where $\b{f}(t): \mathbb{R}_+ \rightarrow \mathbb{R}^N$. Given the initial condition
$\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
\begin{equation}
\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U^* \g{f}(0) = K_t(\L) \b{f}(0),
\end{equation}
which is a convolution of the signal $\b{f}(0)$ with the kernel $K_t(x)=e^{-\tau
t x}$. Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$ that
are one generalization of the squared frequencies on the graph. Hence the kernel $K_t$ is also a generalization of the
Gaussian kernel on the sphere. In \figref{gaussian_filters_comparizon} top, we show
the effect of the convolution by diffusing a unit of heat for $\tau=1$ and various
time $t$. In \figref{gaussian_filters_visualization} of
\ref{sec:filter_visualization}, we show different visualizations of the
convolution kernel $K_t$. We also compare the graph convolution with the
spherical symmetric Gaussian smoothing
(\figref{gaussian_filters_comparizon} bottom) and observe that both
techniques lead to similar results. While the graph convolution is different
from a true spherical convolution, it can, providing the correct
parameterization, well approximate it.

>>>>

Convolutional Neural Networks (CNNs) are now a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence. Despite their successes, they still are mostly developed and applied to regular Euclidean domains such as those supporting images, audio, or video. Unfortunately, in many applications, the data domain is not regular.
As a response to that fact, we are witnessing an increasing interest in the generalization of CNNs to graphs. Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
In this paper we take the latter view and represent a sampled sphere as a graph, for which we define the convolution and pooling operations.
Spherical maps appear in many applications, such as the study of phenomena on the Earth for meteorologists or on the sky for cosmologists.
A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling. Hence, we present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
\nati{I am not that we should talk about pooling in the abstract. Another angle would be to say that HealPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical structure of the Manifold and b) pooling is natural.} 
While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far. 
As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
% The filters learned by the HealpixNet are restricted to being radial.
% Michaël: not necessary in the abstract?
We demonstrate the method on a classification problem of mass maps from two cosmological models. 
\nati{Should we specify what are the baselines? I think not.}
A standard benchmark for that problem is to train an SVM on the histograms of map pixel values. Another is to use the power spectral density instead.
HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
Code and examples are available at \todo{\url{https://github.com/xxx}}.
\end{abstract}

@@

\section{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item make the bibliography display only a few name	
\item (yes) Michael, do you agree with the title HealpixNet? I (Michaël) extensively modified the abstract to reflect that it is a special case of graph CNNs tailored to Healpix. Hence I now agree with the title. Feel free to edit. Ideally I'd like to have "graph" in the title (graph CNNs are quite hot these days), but I couldn't find how.
    \item Emphasize the novelty of using it on Healpix in abstract, into and rest of the paper
    \item add info on comparison with histograms, so that it's just a demonstration
    \item Finish section on Convolutions on graphs (Michael - Nathanael)
    \item finish section on Efficient convolutions (Michael)
    \item (done) Plot of the new filters from Mass maps
    \item (done!, plot to be added) check the power spectrum after smoothing
    \item (done!) upgrade the plot of pooling (Nathanael)
	\item (done!) new plot for network structure (teaser plot) (Michael) What do you think? Todo: link the points on the sphere to the fully connected \nati{I like the plot, but I am thinking about putting multiple spheres with different maps for the convolutiion instead…}
    \item (done!) Figure 1 to be round
    \item (first version done) conclusions
    \item (done!) new simulations with 3 arcmin smoothing
    \item (done!) simulation with cross-validation for the histogram
    \item (done!) Update result section according to the new simulations...
    \item (done!) simulation PSD
    \item (done!) Results figure, add sigma8
    \item (more or less done!) possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael I am not sure about the heat diffusion example...)
\end{itemize}

\begin{figure*}[!ht]
	\centering
	\includegraphics[width=\linewidth]{figures/architecture}
	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier. A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling. While most operations are agnostic to the data domain, the convolution and the down-sampling have to be adapted. In this paper, we propose first to model the sphere with a graph and to perform the convolution on the graph. Graphs are versatile data structures which can model any sampling, even irregular or partial. Second, we propose to exploit a hierarchical pixelization of the sphere for the pooling operation. It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.
    \nati{Great plot! Could you make the sphere round? If you use the current code in paper plot notebook, they will be.}
    }
\end{figure*}

@@

To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling. The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which is efficient and can adapt to any sampling of the sphere. Using a k-nearest neigboors graph, the convolution operation costs $\mathcal{O}(n)$ operations, where $n$ is the number of pixels. This is the lowest possible complexity for a convolution operation without approximations (e.g. by sketching).
The flexibility of modeling the data domain with a graph allows, for example, to easily model data which only spans a part of the sphere, or data which is not uniformly sampled.
Our hierarchical pooling strategy exploits a hierarchical pixelization of the manifold to analyze the data at multiple scales. Such hierarchical pixelizations of the sphere have been well studied.

@@

We give a practical demonstration of the application of our package to cosmological model discrimination using convergence maps, similar to \citep{schmelze2017cosmologicalmodel}.
In a simplified scenario, we classify convergence maps on parts of a sphere into two cosmological models.
These models were designed to have the same power spectrum in range $\ell < 1000$.
We compare the performance of the spherical CNN to a baseline algorithm, an SVM classifier which takes pixel histograms or Power Spectrum Densities (PSD) of these maps as input.
The comparison is made as a function of the noise level on convergence maps and the area of the sphere used. Results show that our model is better at discriminating the maps, is more resilient to noise, and \todo{is faster?}.
\nati{I do not think we should argue for speed gain in this paper. We are probably much more efficient than scnns with the convolution done in the spectral domain. However compared to tradiational methods, we are in most of the cases slower.}

@@

The first approach, leveraging the continuous spherical convolution, has been
proposed by~\cite{cohen2017convolutional,cohen2018spherical}. The goal of
these contributions it to use a rotational equivariant convolution on the
sphere, i.e. a rotation of the input implies the same rotation of the output.
The resulting convolution is performed by a spherical Fourier transform (i.e.
a projection on the spherical harmonics), a  multiplication in the spectral
domain and an inverse spherical Fourier transform. Hence the main
computational cost of a convolution comes from the two Fourier transforms.
Fortunately, the Fourier transform can be accelerated for special samplings
set (theoretically including HealPix, \cite{mohlenkamp1999fast,rokhlin2006fast}). 
The main advantage of this
approach is that it provides a mathematically well defined rotational
equivariant network. Nevertheless, even with these Fourier transform
acceleration, the convolutions remain expensive in comparison to a traditional
2-dimensional convolution, limiting the practical use of this approach.
\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the healpix Fourier transform to get the constants
\nati{@mdeff: for the complexity we probably have $\mathcal{O}(n)$ instead of $\mathcal{O}(n^{3/2})$ (let assume that we have $\approx n^{1/2}$ points allong both axis, computation of the SO3 FFT is composed of 1) $n^{1/2}$ FFTs for a total cost of $n \log (n)$ and 2) $n^{1/2}$ matrix multiplications of size $n^{1/2}$ for a total cost of $n^{3/2}$) For the number, it is a bit more complicated… I guess it is for the next paper.}
}
While a comparison is theoretically possible, the experiments
of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
do not provide any code for the Healpix one. Hence, a practical comparison is
not possible. We also note that this approach cannot be trivially accelerated
if only one part of the sphere is used. This is impractical in the field of
cosmology as the data often observed only on a subpart of the sphere. 
One could still pad the unused part of the sphere with 0. However, this would significantly increase the computational cost of the method.
\nati{@mdeff: do you think we can say the method would be too slow for our dataset even without trying it? I am not so sure...}
\todo{slow: full sky maps are composed of millions of points. partial maps are hard to process}

@@

In an attempt to get the best of the first two approaches, we follow a third
direction. We use a graph to adapt to the particular structure of the sphere.
While the convolution remains efficient, it still captures well the spherical
structure and is particularly adapted to the HealPix sampling.

The use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graph} as well. The authors map omnidirectional images to the sphere, with the goal of correcting for distortions induced by the lens used for the acquisition.
Besides the different application covered by the paper, there are two important
differences. First the sampling is different as~\cite{khasanova2017graph} uses a
grid. Second, it uses a different graph CNN based on a different parameterization
of the convolution kernel.

@@

HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere. As suggested in the name, this pixelization produces a subdivision of a spherical surface in which each pixel covers the same surface area as every other pixel.
The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}). As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
High-resolutions HEALPix maps easily reach millions of pixels. \figref{example_maps} shows two examples.
Another property of the HEALPix grid is that the pixel centers, represented by the black dots in \figref{pooling}, occur on a discrete number of rings of constant latitude (the number of which depends on the resolution).
\nati{The figure is beautiful, but should we really show it? If we target cosmologists, we can simply list some type of data. If we target a broader audience, maybe it makes sense to provide some illustration.}

@@

In the classical 2-dimensional convolution, each pixel is connected with the
same weight to its 4 closest neighbors. We use a weighted undirected graph to
generalize this idea to the ubiquitous HealPix
sampling~\citep{gorski2005healpix}.  Each pixel is represented by a node
(vertex) connected to his $8$ or $7$ closest neighbors.\footnote{For some
pixels, the $8^{th}$ nearest neighbor is not well defined.} Given the set of
nearest neighbors, we define the weight matrix $W$ using the following scheme
\begin{equation}
W[i,j]=\begin{cases}
e^{-\frac{\|x_i-x_j\|_2^2}{\sigma^2}} & \text{if pixels $i$ and $j$ are connected, and}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}
\todo{why not $1/d$? See Pascal's paper, \nati{ The question is: is $1/d$ also good when we have 7/8 neighboors instead of 4? Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment. We probably do not have to change any parameter though... @mdeff: do you think we should try this for this paper? Or we keep that for the next one.}}
Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$
on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected
pixels $i$ and $j$. This weighting scheme is important as the distances between
pixels varies due to the small sampling irregularities. Some of the
irregularities have been highlighted in the graph displayed in
\figref{healpix_graph_4}.

@@

\begin{figure}[!ht]
\centering
% \includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
\vspace{-0.5cm}
\includegraphics[width=0.35\textwidth]{figures/half_graph_4.pdf}
\vspace{-0.5cm}
\caption{
Top view of a Healpix graph for half the sphere using a HealPix nside parameter of $4$.
Nodes with 7 neighbors are highlighted. \label{fig:healpix_graph_4}
}

@@

As shown in \figref{graph_harmonics}, it turns out that using the graph
construction described above, the graph Fourier harmonics resemble the
classical spherical harmonics giving us an indication that the graph is able to
capture the spherical properties of the Healpix sampling. This topic is further discussed in Appendix~\ref{sec:spherical_harmonics}.

@@

\paragraph{Example:}
Let us consider the heat diffusion problem
\begin{equation} \label{eqn:heat_equation}
\L \b{f}(t) = \tau \partial_t \b{f}(t),
\end{equation}
where $\b{f}(t): \mathbb{R}_+ \rightarrow \mathbb{R}^N$. Given the initial condition
$\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
\begin{equation}
\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U^* \g{f}(0) = K_t(\L) \b{f}(0),
\end{equation}
which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(x)=e^{-\tau
t x}$. Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$. They are a generalization of the squared frequencies in the graph setting. Hence the kernel $K_t$ can also be considered as a generalization of the
Gaussian kernel on the sphere. In \figref{gaussian_filters_comparizon} top, we show
the effect of the convolution by diffusing a unit of heat for $\tau=1$ and various
time $t$. We also compare the graph convolution with the
spherical symmetric Gaussian smoothing
(\figref{gaussian_filters_comparizon} bottom) and observe that both
techniques lead to similar results. While the graph convolution is different
from a true spherical convolution, it can, providing the correct
parameterization, well approximate it.
In~\figref{gaussian_filters_visualization} of Appendix~\ref{sec:filter_visualization}, we provide additional visualizations of the
convolution kernel $K_t$.
